---
title: "geniusProva"
author: "cla"
date: "8/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(genius)
library(dplyr)
#library(learnr)
#learnr::run_tutorial("genius_tutorial", "genius")

```


```{r}
august = genius_lyrics("taylor swift", "august")
august
betty = genius_lyrics("taylor swift", "betty")
betty
folklore = genius_album("taylor swift", "folklore")
folklore
evermore = genius_tracklist(artist = "Taylor Swift", album = "evermore") 
e = evermore
evermore%>%
  select(track_title)

```

A common use for lyric analysis is to compare the lyrics of one artist to another. In order to do that, you could potentially retrieve the lyrics for multiple songs and albums and then join them together. This has one major issue in my mind, it makes you create multiple object taking up precious memory. For this reason, the function add_genius() was developed. This enables you to create a tibble with a column for an artists name and their album or song title. add_genius() will then go through the entire tibble and add song lyrics for the tracks and albums that are available.

Let’s try this with a tibble of three songs.
```{r}
three_songs <- tribble(
  ~ artist, ~ title,
  "Big Thief", "UFOF",
  "Andrew Bird", "Imitosis",
  "Sylvan Esso", "Slack Jaw"
)

song_lyrics <- three_songs %>% 
  add_genius(artist, title, type = "lyrics")

song_lyrics %>% 
  count(artist)



```

add_genius() also extends this functionality to albums.
```{r}
albums <- tribble(
  ~ artist, ~ title,
  "Andrew Bird", "Armchair Apocrypha",
  "Andrew Bird", "Things are really great here sort of"
)

album_lyrics <- albums %>% 
  add_genius(artist, title, type = "album")

album_lyrics
```
In the scenario that you want to mix single songs and lyrics, you can supply a column with the type value of each row. The example below illustrates this. First a tibble with artist, track or album title, and type columns are created. Next, the tibble is piped to add_genius() with the unquote column names for the artist, title, and type columns. This will then iterate over each row and fetch the appropriate song lyrics.
```{r}
song_album <- tribble(
  ~ artist, ~ title, ~ type,
  "Big Thief", "UFOF", "lyrics",
  "Andrew Bird", "Imitosis", "lyrics",
  "Sylvan Esso", "Slack Jaw", "lyrics",
  "Movements", "Feel Something", "album"
)

mixed_lyrics <- song_album %>% 
  add_genius(artist, title, type)
```


```{r}
charts = read.csv("charts.csv")
charts
data = read.csv("data.csv")
data
tracks = read.csv("tracks_features.csv")
tracks
billboard = read.csv("billboardHot100_1999-2019.csv")
billboard



```

```{r}
library(devtools)
devtools::install_github('charlie86/spotifyr')
```

